Development of a 3D display

### 2016-05-14 paper.tex
Removed trailing whitespace
Nicer signature field
Fixed math error

\vspace{10mm}
\noindent Location and Date: \hspace{0.35\textwidth} Signed:\\
\rule[3mm]{\textwidth}{0.5pt}

@@

\begin{ownmath}
\textrm{P\textsubscript{MAX}} = (\SI{5}{\volt} - \textrm{V\textsubscript{F}}) * 
\SI{20.6}{\milli\ampere\per output} * \SI{16}{outputs} = \SI{867.9}{\milli\watt}
\end{ownmath}

@@

A power output of almost a watt is not to be underestimated, and tests have shown that that the
boards do get quite hot when operated at full power. In reality, however, the situation is much
less severe because the LEDs are typically turned on only during a fraction of the rotation.
Furthermore, the quick rotation results in excellent air circulation, which aids the dissipation
of heat.

>>>>

\vspace{10mm}
\rule{\textwidth}{0.5pt}
\begin{minipage}[t]{0.5\textwidth}
Location and Date
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\hspace{-1mm}Signature
\end{minipage}

@@

\begin{ownmath}
\textrm{P\textsubscript{MAX}} = (\SI{5}{\volt} - \textrm{V\textsubscript{F}}) *
\SI{20.6}{\milli\ampere\per output} * \SI{16}{outputs} = \SI{780}{\milli\watt}
\end{ownmath}

@@

A power output of \SI{780}{\milli\watt} is not to be underestimated on such a small PCB, and tests
have shown that that the boards do get quite hot when operated at full power. In reality, however,
the situation is much less severe because the LEDs are typically turned on only during a fraction
of the rotation. Furthermore, the quick rotation results in excellent air circulation, which aids
the dissipation of heat.
